\name: Combining Bottom-up and top-down approaches through graph learning over interaction networks for drug-target-interaction prediction

### 2021-02-07 paper/main.tex
siamese question

As we want to learn from the similarity of drug side effects and
protein phenotypes, we use a deep Siamese neural network.
A Siamese neural network aims to learn a similarity between two
embeddings.

learning a high-dimensional embedding emphasizing this identity by
forcing a similarity between these embeddings. On the other hand we
built a deep neural network for the molecular structure based
features, also benefiting from the siamese network
architecture. Computing the similarity between two representations,
allows for a variety of different methods.  However, we decided for
the cosine similarity measure being invariant to scaling.

>>>>

\todo[inline]{Looking at the code, I wonder if what is implemented is
  actually a Siamese ANN; it does not look as if the weights are
  shared between the two networks, so looks more like a twin or
  half-twin network?}

As we want to learn from the similarity of drug side effects and
protein phenotypes, we use a deep Siamese neural network with
a contrastive loss using cosine similarity.
A Siamese neural network aims to learn a similarity between two
embeddings.

% learning a high-dimensional embedding emphasizing this identity by
% forcing a similarity between these embeddings. On the other hand we
% built a deep neural network for the molecular structure based
% features, also benefiting from the siamese network
% architecture. Computing the similarity between two representations,
% allows for a variety of different methods.  
% However, we decided for
% the cosine similarity measure being invariant to scaling.
